---
title: "Describe Cohorts"
author: "Chase Latour"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(targets)
library(tidyverse)
library(kableExtra)
```

# Objetives

The goal of this program is to describe the pregnancy cohorts created for each analytic dataset.

# Data

First, we must read in the necessary data files. 

```{r}

describe <- tar_read(all_descriptives)

analyses <- tar_read(all_analyses)

```

# Functions

Make a function that outputs a table describing a DGM

```{r}


describe_cohorts <- function(describe_subset){
  
  hold <- describe_subset %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           missing_mar, missing_mnar, trt,
           n_low, n_med, n_high, 
           n_miscarriage_all, n_stillbirth_all, n_livebirth_all) %>% 
    kbl() %>%
    collapse_rows(col_names = c(pnc_wk, marginal_p_miss_severity, marginal_p_miss_miscarriage),
                  valign = "top") %>%
    kable_classic()
  
  return(hold)
  
}

```

Make a function that outputs the analytic results for a DGM

```{r}

# First, prepare the dataset
analyses2 <- analyses %>% 
  mutate(
    truth = map(potential_risks, ~.x %>% rename_with(~paste0("truth_", .))),
    observed_del = map(observed_deliveries, ~.x %>%  rename_with(~paste0("obs_del_", .))),
    observed_out = map(observed_outcomes, ~.x %>% rename_with(~paste0("obs_out_", .))),
    tte = map(tte, ~.x %>% rename_with(~paste0("all_preg_", .))),
    all_outc = map(sens_anal_all_outc, ~.x %>% rename_with(~paste0("all_preg_all_outc_", .))),
    trt_outc = map(sens_anal_trt_outc, ~.x %>% rename_with(~paste0("trt_preg_outc_", .))),
    untrt_outc = map(sens_anal_untrt_out, ~.x %>% rename_with(~paste0("untrt_preg_outc_", .))),
    no_outc = map(sens_anal_no_outc, ~.x %>% rename_with(~paste0("all_preg_no_outc_", .)))
  ) %>% 
  select(rr_abortion, rr_preec, marginal_p_miss_severity, marginal_p_miss_miscarriage,
         truth, observed_del, observed_out, tte, all_outc, trt_outc, untrt_outc, no_outc) %>% 
  unnest(c(truth, observed_del, observed_out, tte, all_outc, trt_outc, untrt_outc, no_outc)) %>% 
  # select(-c(ends_with("pnc_wk"), ends_with("risk0"), ends_with("risk1")))
  mutate(
    marginal_p_miss_severity = marginal_p_miss_severity, #1.13,
    marginal_p_miss_miscarriage = marginal_p_miss_miscarriage / 4.9
  ) 


print_analysis_kable_del <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           obs_del_risk0, obs_del_risk1, obs_del_rd, obs_del_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      "Observed Deliveries" = 4 #,
      # "Observed Outcomes" = 4,
      # "All Pregnancies" = 4,
      # "All Pregnancies, Assuming All Censored had Outcome" = 4,
      # "All Pregnancies, Assuming Treated had Outcome" = 4,
      # "All Pregnancies, Assumine Untreated had Outcome" = 4,
      # "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}


print_analysis_kable_outc <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           obs_out_risk0, obs_out_risk1, obs_out_rd, obs_out_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      # "Observed Deliveries" = 4 #,
      "Observed Outcomes" = 4 #,
      # "All Pregnancies" = 4,
      # "All Pregnancies, Assuming All Censored had Outcome" = 4,
      # "All Pregnancies, Assuming Treated had Outcome" = 4,
      # "All Pregnancies, Assumine Untreated had Outcome" = 4,
      # "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}


print_analysis_kable_all <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           all_preg_risk0, all_preg_risk1, all_preg_rd, all_preg_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      # "Observed Deliveries" = 4 #,
      # "Observed Outcomes" = 4 #,
      "All Pregnancies" = 4 #,
      # "All Pregnancies, Assuming All Censored had Outcome" = 4,
      # "All Pregnancies, Assuming Treated had Outcome" = 4,
      # "All Pregnancies, Assuming Untreated had Outcome" = 4,
      # "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}


print_analysis_kable_all_outc <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           all_preg_all_outc_risk0, all_preg_all_outc_risk1, all_preg_all_outc_rd, all_preg_all_outc_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      # "Observed Deliveries" = 4 #,
      # "Observed Outcomes" = 4 #,
      # "All Pregnancies" = 4 #,
      "All Pregnancies, Assuming All Censored had Outcome" = 4 #,
      # "All Pregnancies, Assuming Treated had Outcome" = 4,
      # "All Pregnancies, Assuming Untreated had Outcome" = 4,
      # "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}


print_analysis_kable_trt_outc <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           trt_preg_outc_risk0, trt_preg_outc_risk1, trt_preg_outc_rd, trt_preg_outc_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      # "Observed Deliveries" = 4 #,
      # "Observed Outcomes" = 4 #,
      # "All Pregnancies" = 4 #,
      # "All Pregnancies, Assuming All Censored had Outcome" = 4 #,
      "All Pregnancies, Assuming Treated had Outcome" = 4 #,
      # "All Pregnancies, Assuming Untreated had Outcome" = 4,
      # "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}



print_analysis_kable_untrt_outc <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           untrt_preg_outc_risk0, untrt_preg_outc_risk1, untrt_preg_outc_rd, untrt_preg_outc_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      # "Observed Deliveries" = 4 #,
      # "Observed Outcomes" = 4 #,
      # "All Pregnancies" = 4 #,
      # "All Pregnancies, Assuming All Censored had Outcome" = 4 #,
      # "All Pregnancies, Assuming Treated had Outcome" = 4 #,
      "All Pregnancies, Assuming Untreated had Outcome" = 4 #,
      # "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}




print_analysis_kable_no_outc <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    select(marginal_p_miss_severity, marginal_p_miss_miscarriage,
           truth_risk0, truth_risk1, truth_rd, truth_rr,
           all_preg_no_outc_risk0, all_preg_no_outc_risk1, all_preg_no_outc_rd, all_preg_no_outc_rr) %>% 
    kbl(col.names = NA) %>% # 
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "$$RD$$" = 1,
      "$$RR$$" = 1), 2)# 8)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      # "Observed Deliveries" = 4 #,
      # "Observed Outcomes" = 4 #,
      # "All Pregnancies" = 4 #,
      # "All Pregnancies, Assuming All Censored had Outcome" = 4 #,
      # "All Pregnancies, Assuming Treated had Outcome" = 4 #,
      # "All Pregnancies, Assuming Untreated had Outcome" = 4 #,
      "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}





```

Make a function that outputs figures of the parameters. 

```{r}

# Prep the dataset for figures

figure_data <- analyses2 %>% 
  pivot_longer(
    cols = !c(rr_abortion, rr_preec, marginal_p_miss_severity, marginal_p_miss_miscarriage),
    names_to = "estimate",
    values_to = "value"
  ) %>% 
  mutate(
    Cohort = case_when(grepl("truth", estimate) ~ "Truth",
                       grepl("obs_del", estimate) ~ "Observed Deliveries",
                       grepl("obs_out", estimate) ~ "Observed Outcomes",
                       grepl("all_preg_all_outc", estimate) ~ "Sens: All Pregnancies Outcome",
                       grepl("untrt_preg_outc", estimate) ~ "Sens: Untrt Pregnancies Outcome",
                       grepl("trt_preg_outc", estimate) ~ "Sens: Trt Pregnancies Outcome",
                       grepl("all_preg_no_outc", estimate) ~ "Sens: All Pregnancies No Outcome",
                       grepl("all_preg", estimate) ~ "All Pregnancies: TTE"),
    parameter = case_when(grepl("_risk0", estimate) ~ "Risk, Non-Initiators",
                          grepl("_risk1", estimate) ~ "Risk, Initiators",
                          grepl("_rd", estimate) ~ "Risk Difference",
                          grepl("_rr", estimate) ~ "Risk Ratio"),
    missing = paste0(marginal_p_miss_severity,"/", marginal_p_miss_miscarriage) ,
    missing = factor(missing,
                     levels = c("0/0.05", "0.025/0.025", "0.05/0",
                                "0/0.2",  "0.1/0.1",     "0.2/0"))
  )

truths <- figure_data %>% 
  filter(Cohort == "Truth") %>% 
  rename(truth = value) %>% 
  select(rr_abortion, rr_preec, missing, parameter, truth)

estimates <- figure_data %>% 
  filter(Cohort != "Truth")

figure_data2 <- left_join(estimates, truths, by = c("rr_abortion", "rr_preec",
                                                    "missing", "parameter")) %>% 
  mutate(
    scenario = case_when(
      rr_abortion == 0.5 ~ "Initiation decreases risk of miscarriage",
      rr_abortion == 1.0 ~ "Initiation does not affect risk of miscarriage",
      rr_abortion == 2.0 ~ "Initiation increases risk of miscarriage"
    )
  )


create_figure_nosens <- function(dataset, parameter, rr_preec, title){
  
  param <- sym(parameter)
  # rr_abort <- sym(rr_abort)
  rr_preeclampsia <- sym(rr_preec)
  
  plot <- dataset %>%
    filter(!grepl("Sens", Cohort)) %>% 
    filter(rr_preec == rr_preeclampsia) %>%
    filter(parameter == param) %>% 
    ggplot(aes(x = missing, y = value, color = Cohort, shape = Cohort)) + # , shape = cohort
    geom_point(size = 3, position = position_dodge(0.5)) +
    facet_wrap(scenario ~., nrow = 1) +
    geom_hline(aes(yintercept = truth), col = "red", linetype = "dashed") + 
    # ggtitle(bquote(.(param) ~ ": " ~ RR[Abortion] == .(rr_abortion) ~ 
    #                " and " ~ RR[Preeclampsia] == .(rr_preeclampsia))) +
    xlab("Approximate Percent Missing Due to Severity/Abortion") + 
    ylab("Parameter Estimate") +
    ggtitle(parameter)
  
  if (parameter == "Risk Ratio") {
    plot <- plot + scale_y_log10() 
  }
  
  return(plot)
  
}




create_figure_sens <- function(dataset, parameter, rr_preec, title){
  
  param <- sym(parameter)
  # rr_abort <- sym(rr_abort)
  rr_preeclampsia <- sym(rr_preec)
  
  plot <- dataset %>%
    # filter(!grepl("Sens", Cohort)) %>% 
    mutate(Analysis = ifelse(grepl("Sens", Cohort),
                             "Sensitivity Analysis",
                             "Primary Analysis")) %>% 
    filter(rr_preec == rr_preeclampsia) %>%
    filter(parameter == param) %>% 
    ggplot(aes(x = missing, y = value, color = Cohort, shape = Analysis)) + # , shape = cohort
    geom_point(size = 3, position = position_dodge(0.5)) +
    facet_wrap(scenario ~., nrow = 1) +
    geom_hline(aes(yintercept = truth), col = "red", linetype = "dashed") + 
    # ggtitle(bquote(.(param) ~ ": " ~ RR[Abortion] == .(rr_abortion) ~ 
    #                " and " ~ RR[Preeclampsia] == .(rr_preeclampsia))) +
    xlab("Approximate Percent Missing Due to Severity/Abortion") + 
    ylab("Parameter Estimate") +
    ggtitle(parameter)
  
  if (parameter == "Risk Ratio") {
    plot <- plot + scale_y_log10()
  }
  
  return(plot)
  
}




```


# Output Tabular Results
Create kable with description of a specified dataset. Do this for each RR combination.

## $RR_{Abortion} = 0.5, RR_{Preeclampsia} = 0.5$

```{r}
    
describe %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_del()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_all()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_all_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_trt_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_untrt_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 0.5) %>% 
  print_analysis_kable_no_outc()



```


## $RR_{RR_{Abortion} = 1.0, Preeclampsia} = 0.5$

```{r}
    
describe %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_del()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_all()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_all_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_trt_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_untrt_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.5) %>% 
  print_analysis_kable_no_outc()

```


## $RR_{RR_{Abortion} = 2.0, Preeclampsia} = 0.5$

```{r}
    
describe %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_del()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_all()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_all_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_trt_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_untrt_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 0.5) %>% 
  print_analysis_kable_no_outc()

```


## $RR_{Abortion} = 0.5, RR_{Preeclampsia} = 1.0$

```{r}
    
describe %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_del()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_all()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_all_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_trt_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_untrt_outc()

analyses2 %>% 
  filter(rr_abortion == 0.5 & rr_preec == 1.0) %>% 
  print_analysis_kable_no_outc()



```


## $RR_{RR_{Abortion} = 1.0, Preeclampsia} = 1.0$

```{r}
    
describe %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_del()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_all()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_all_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_trt_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_untrt_outc()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable_no_outc()

```


## $RR_{RR_{Abortion} = 2, Preeclampsia} = 1.0$

```{r}
    
describe %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_del()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_all()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_all_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_trt_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_untrt_outc()

analyses2 %>% 
  filter(rr_abortion == 2 & rr_preec == 1.0) %>% 
  print_analysis_kable_no_outc()


```


# Output Figures

## Without Sensitivity Analyses

### Initiation Decreases Risk of Preeclampsia

```{r}

create_figure_nosens(figure_data2 %>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"), 
              "Risk, Initiators", "0.5")
create_figure_nosens(figure_data2%>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"),
                       "Risk, Non-Initiators", "0.5")
create_figure_nosens(figure_data2, "Risk Difference", "0.5")
create_figure_nosens(figure_data2, "Risk Ratio", "0.5")

```

### Initiation Does not Affect Risk of Preeclampsia

```{r}

create_figure_nosens(figure_data2 %>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"), 
              "Risk, Initiators", "1")
create_figure_nosens(figure_data2%>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"),
                       "Risk, Non-Initiators", "1")
create_figure_nosens(figure_data2, "Risk Difference", "0.5", "1")
create_figure_nosens(figure_data2, "Risk Ratio", "0.5", "1")

```


## With Sensitivity Analyses

### Initiation Decreases Risk of Preeclampsia

```{r}

create_figure_sens(figure_data2 %>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"), 
              "Risk, Initiators", "0.5")
create_figure_sens(figure_data2%>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"),
                       "Risk, Non-Initiators", "0.5")
create_figure_sens(figure_data2, "Risk Difference", "0.5")
create_figure_sens(figure_data2, "Risk Ratio", "0.5")

```

### Initiation Does not Affect Risk of Preeclampsia

```{r}

create_figure_sens(figure_data2 %>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"), 
              "Risk, Initiators", "1")
create_figure_sens(figure_data2%>% 
                filter(Cohort != "Sens: Trt Pregnancies Outcome" & 
                         Cohort != "Sens: Untrt Pregnancies Outcome"),
                       "Risk, Non-Initiators", "1")
create_figure_sens(figure_data2, "Risk Difference", "0.5", "1")
create_figure_sens(figure_data2, "Risk Ratio", "0.5", "1")

```

