---
title: "Describe Cohorts"
author: "Chase Latour"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(targets)
library(tidyverse)
library(kableExtra)
```

# Objetives

The goal of this program is to describe the pregnancy cohorts created for each analytic dataset.

# Data

First, we must read in the necessary data files. 

```{r}

describe <- tar_read(all_descriptives)

analyses <- tar_read(all_analyses)

```

# Functions

Make a function that outputs a table describing a DGM

```{r}

describe_cohorts <- function(describe_subset){
  
  hold <- describe_subset %>% 
    select(pnc_wk, marginal_p_miss_severity, marginal_p_miss_miscarriage,
           trt, n_low:missing_mnar_t) %>% 
    kbl() %>%
    collapse_rows(col_names = c(pnc_wk, marginal_p_miss_severity, marginal_p_miss_miscarriage),
                  valign = "top") %>%
    kable_classic()
  
  return(hold)
  
}

```

Make a function that outputs the analytic results for a DGM

```{r}

# First, prepare the dataset
analyses2 <- analyses %>% 
  mutate(
    # truth_r0 = map_dbl(potential_risks, ~subset(.x, pnc_wk == "all")$risk0)
    truth = map(potential_risks, ~.x %>% rename_with(~paste0("truth_", .))),
    observed_del = map(observed_deliveries, ~.x %>%  rename_with(~paste0("obs_del_", .))),
    observed_out = map(observed_outcomes, ~.x %>% rename_with(~paste0("obs_out_", .))),
    tte = map(tte, ~.x %>% rename_with(~paste0("all_preg_", .))),
    tte_all_outc = map(sens_anal_all_outc, ~.x %>% rename_with(~paste0("all_preg_all_outc_", .))),
    tte_no_outc = map(sens_anal_no_outc, ~.x %>% rename_with(~paste0("all_preg_no_outc_", .)))
  ) %>% 
  select(rr_abortion, rr_preec, marginal_p_miss_severity, marginal_p_miss_miscarriage,
         truth, observed_del, observed_out, tte, tte_all_outc, tte_no_outc) %>% 
  unnest(c(truth, observed_del, observed_out, tte, tte_all_outc, tte_no_outc)) %>% 
  # select(-c(ends_with("pnc_wk"), ends_with("risk0"), ends_with("risk1")))
  mutate(
    marginal_p_miss_severity = marginal_p_miss_severity / 1.13,
    marginal_p_miss_miscarriage = marginal_p_miss_miscarriage / 4.9
  ) 

# Now, output a kable
print_analysis_kable <- function(data_subset){
  
  hold <- data_subset %>% 
    mutate(across(truth_risk0:all_preg_no_outc_rr, ~round(.x, 3))) %>% 
    select(!c(rr_abortion, rr_preec)) %>% 
    kbl() %>% # col.names = NA
    collapse_rows(columns = 1:2,
                  valign = "top") %>%
    kable_classic() %>% 
    add_header_above(c(
      "Prob Missing Due to Severity" = 1,
      "Prob Missing Due to Abortion" = 1,
      rep(c("$$Risk_0$$" = 1,
      "$$Risk_1$$" = 1,
      "RD" = 1,
      "RR = 1"),6)
    )) %>% 
    add_header_above(c(
      " " = 2,
      "Truth" = 4,
      "Observed Deliveries" = 4,
      "Observed Outcomes" = 4,
      "All Pregnancies" = 4,
      "All Pregnancies, Assuming All Censored had Outcome" = 4,
      "All Pregnancies, Assuming All Censored did not have Outcome" = 4
    ))
  
  return(hold)
  
}


```

Make a function that outputs figures of the parameters. 

```{r}

# Prep the dataset for figures

figure_data <- analyses2 %>% 
  pivot_longer(
    cols = !c(rr_abortion, rr_preec, marginal_p_miss_severity, marginal_p_miss_miscarriage),
    names_to = "estimate",
    values_to = "value"
  ) %>% 
  mutate(
    cohort = case_when(grepl("truth", estimate) ~ "Truth",
                       grepl("obs_del", estimate) ~ "Observed Deliveries",
                       grepl("obs_out", estimate) ~ "Observed Outcomes",
                       grepl("all_preg_all_outc", estimate) ~ "All Pregnancies: All Outcome",
                       grepl("all_preg_no_outc", estimate) ~ "All Pregnancies: No Outcome",
                       grepl("all_preg", estimate) ~ "All Pregnancies: TTE"),
    parameter = case_when(grepl("_risk0", estimate) ~ "Risk, Non-Initiators",
                          grepl("_risk1", estimate) ~ "Risk, Initiators",
                          grepl("_rd", estimate) ~ "Risk Difference",
                          grepl("_rr", estimate) ~ "Risk Ratio"),
    missing = paste0(marginal_p_miss_severity,"/", marginal_p_miss_miscarriage) ,
    missing = factor(missing,
                     levels = c("0/0.05", "0.025/0.025", "0.05/0",
                                "0/0.2",  "0.1/0.1",     "0.2/0"))
  )

truths <- figure_data %>% 
  filter(cohort == "Truth") %>% 
  rename(truth = value) %>% 
  select(rr_abortion, rr_preec, missing, parameter, truth)

estimates <- figure_data %>% 
  filter(cohort != "Truth")

figure_data2 <- left_join(estimates, truths, by = c("rr_abortion", "rr_preec",
                                                    "missing", "parameter"))

create_figure <- function(dataset, parameter, rr_abort, rr_preec){
  
  param <- sym(parameter)
  rr_abort <- sym(rr_abort)
  rr_preeclampsia <- sym(rr_preec)
  
  plot <- figure_data2 %>%
    filter(rr_abortion == rr_abort & rr_preec == rr_preeclampsia) %>%
    filter(parameter == param) %>% 
    ggplot(aes(x = missing, y = value, color = cohort, shape = cohort)) +
    geom_point(size = 3, position = position_dodge(0.5)) +
    facet_wrap(parameter ~., ncol = 1) +
    geom_hline(aes(yintercept = truth), col = "red", linetype = "dashed") + 
    ggtitle(bquote(.(param) ~ ": " ~ RR[Abortion] == .(rr_abort) ~ 
                   " and " ~ RR[Preeclampsia] == .(rr_preeclampsia))) +
    xlab("Approximate Percent Missing Due to Severity/Abortion") + 
    ylab("Parameter Estimate")
  
  return(plot)
  
}

```


# Output Results
Create kable with description of a specified dataset. Do this for each RR combination.

## $RR_{Abortion} = 0.7, RR_{Preeclampsia} = 0.7$

```{r}
    
describe %>% 
  filter(rr_abortion == 0.7 & rr_preec == 0.7) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 0.7 & rr_preec == 0.7) %>% 
  print_analysis_kable()

# Risks
create_figure(figure_data2, "Risk, Initiators", "0.7", "0.7")
create_figure(figure_data2, "Risk, Non-Initiators", "0.7", "0.7")
create_figure(figure_data2, "Risk Difference", "0.7", "0.7")
create_figure(figure_data2, "Risk Ratio", "0.7", "0.7")

```


## $RR_{RR_{Abortion} = 1.0, Preeclampsia} = 0.7$

```{r}
    
describe %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.7) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 0.7) %>% 
  print_analysis_kable()

# Risks
create_figure(figure_data2, "Risk, Initiators", "1", "0.7")
create_figure(figure_data2, "Risk, Non-Initiators", "1", "0.7")
create_figure(figure_data2, "Risk Difference", "1", "0.7")
create_figure(figure_data2, "Risk Ratio", "1", "0.7")

```


## $RR_{RR_{Abortion} = 1.5, Preeclampsia} = 0.7$

```{r}
    
describe %>% 
  filter(rr_abortion == 1.5 & rr_preec == 0.7) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 1.5 & rr_preec == 0.7) %>% 
  print_analysis_kable()

# Risks
create_figure(figure_data2, "Risk, Initiators", "1.5", "0.7")
create_figure(figure_data2, "Risk, Non-Initiators", "1.5", "0.7")
create_figure(figure_data2, "Risk Difference", "1.5", "0.7")
create_figure(figure_data2, "Risk Ratio", "1.5", "0.7")

```


## $RR_{Abortion} = 0.7, RR_{Preeclampsia} = 1.0$

```{r}
    
describe %>% 
  filter(rr_abortion == 0.7 & rr_preec == 1.0) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 0.7 & rr_preec == 1.0) %>% 
  print_analysis_kable()

# Risks
create_figure(figure_data2, "Risk, Initiators", "0.7", "1")
create_figure(figure_data2, "Risk, Non-Initiators", "0.7", "1")
create_figure(figure_data2, "Risk Difference", "0.7", "1")
create_figure(figure_data2, "Risk Ratio", "0.7", "1")

```


## $RR_{RR_{Abortion} = 1.0, Preeclampsia} = 1.0$

```{r}
    
describe %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 1.0 & rr_preec == 1.0) %>% 
  print_analysis_kable()

# Risks
create_figure(figure_data2, "Risk, Initiators", "1", "1")
create_figure(figure_data2, "Risk, Non-Initiators", "1", "1")
create_figure(figure_data2, "Risk Difference", "1", "1")
create_figure(figure_data2, "Risk Ratio", "1", "1")

```


## $RR_{RR_{Abortion} = 1.5, Preeclampsia} = 1.0$

```{r}
    
describe %>% 
  filter(rr_abortion == 1.5 & rr_preec == 1.0) %>% 
  describe_cohorts()

analyses2 %>% 
  filter(rr_abortion == 1.5 & rr_preec == 1.0) %>% 
  print_analysis_kable()

# Risks
create_figure(figure_data2, "Risk, Initiators", "1.5", "1")
create_figure(figure_data2, "Risk, Non-Initiators", "1.5", "1")
create_figure(figure_data2, "Risk Difference", "1.5", "1")
create_figure(figure_data2, "Risk Ratio", "1.5", "1")

```