---
title: "create cohorts - review"
author: "Chase Latour"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: "hide"
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Pull in the necessary libraries
library(tidyverse)
library(readxl)

```

# Summary

The goal of this program is to create the super cohorts for each of the data generating models

First, we pull in the files that we need (i.e., files where functions are stored).

```{r}

# Pull in the data generation functions - These functions create the raw data
source("Data generation functions.R")

# Pull in the cohort creation functions - These functions actually create the analytic cohorts from the raw data
source("create cohort functions.R")

```

Create a function that generates the data for each scenario

```{r}

# Set values that are going to hold for ALL DGMs and analytic samples
p_sev <- 1 - 0.9^(1/40) # Weekly prob (over 40 weeks) of being LTFU at lowest severity
b0_sev <- log(p_sev / (1-p_sev)) # beta 0 in the logistic regression for LTFU due to severity is NOT varied across scenarios


# Function can be used to generate each scenario with the specified inputs.
generate_scenario <- function(param_file, b0_sev, beta12, save_name_gen, 
                              gamma0, gamma1, save_name_cohort,
                              rr_abortion, rr_preec){
  
  ## Create the parameter list
  params_list_gen <- list(
    n_sim = 1,
    n = 1200,
    p_sev_beta = c(b0_sev, log(beta12 / (1-beta12)), log((2*beta12 / (1 - (2*beta12))))),
    p_trt_sev = c(0.35, 0.50, 0.65),
    p_indx_pnc = c(0.25, 0.375, 0.375)
  )
  
  ## Create p_miss_outcome - for logistic regression to determine LTFU due to missing outcome
  p_miss_outcome <- c(log(gamma0 / (1-gamma0)), log(gamma1/(1-gamma1)))
  
  ## Upload the parameter Excel files.
  potential_preg_untrt <- read_xlsx(param_file, sheet = "potential_preg_untrt")
  potential_preg_trt <- read_xlsx(param_file, sheet = "potential_preg_trt")
  potential_preec_untrt <- read_xlsx(param_file, sheet = "potential_preec_untrt")
  potential_preec_trt <- read_xlsx(param_file, sheet = "potential_preec_trt")
  revised_preg <- read_xlsx(param_file, sheet = "postpreec_preg")
  pnc_prob <- read_xlsx(param_file, sheet = "pnc_prob")
  
  ## Generate all the potential outcomes
  
  all_outcomes <- do.call(generate, params_list_gen) %>% 
    # Save the data generation values
    mutate(rr_trt_abortion = rr_abortion,
           rr_trt_preec = rr_preec,
           diff_beta1_beta2 = beta12,
           gamma_0 = gamma0,
           gamma_1 = gamma1)
  
  # Save the RDS file -- Potentially important for bootstrapping SEs
  saveRDS(all_outcomes, save_name_gen)
  
  p_miss_outcome <- c(log(gamma0 / (1-gamma0)), log(gamma1 / (1-gamma1)))
  
  ## Select the observed cohort
  all_outcomes2 <- create_cohort(all_outcomes, p_miss_outcome)
  
  # Save the RDS file
  saveRDS(all_outcomes2, save_name_cohort)
  
}


```

# $RR_{Trt-Abortion}=0.8$, $RR_{Trt-Preeclampsia}=0.8$

All DGMs fitting these criteria will use the same parameter file, as specified below.

```{r}

param_file <- "Parameters_Abortion0_8_Preeclampsia0_8.xlsx"

```

## $\beta_1 = 0.01$, $\beta_2 = 0.02$, $\gamma_0 = 0.1$, $\gamma_1 = 0.001$

Generate the analytic samples where $\beta1 = 0.01, \beta_2 = 0.02, \gamma_0 = 0.1, \text{ and } \gamma_1 = 0.001$.

```{r}

# Specify values 
save_name_gen <- "ab08preec08_beta001_gamma01_001_gen.rds"
beta12 <- 0.01
gamma0 <- 0.1
gamma1 <- 0.001
save_name_cohort <- "ab08preec08_beta001_gamma01_001_cohort.rds"

set.seed(1234)

generate_scenario(param_file, b0_sev, 
                  beta12, save_name_gen,
                  gamma0, gamma1, save_name_cohort,
                  rr_abortion, rr_preec)

```
