---
title: "Describe Cohorts"
author: "Chase Latour"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

# Objetives

The goal of this program is to describe the pregnancy cohorts created for each analytic dataset.

# Data

First, we must read in the necessary data files. 

```{r}


describe <- do.call(rbind, readRDS("data/ab08preec08_beta001_gamma01_001.rds")) %>% 
  mutate(scenario = "test1")


```

# Functions

Create kable with description of a specified dataset.

```{r}

describe_cohort <- function(dataset){
  
  hold <- dataset %>% #  test2 %>%
    group_by(scenario, trt) %>% 
    summarize(
      
      # Calculate the number per category
      n_low = sum(severity == 0),
      n_low_perc = round(100*n_low/n(),2),
      n_med = sum(severity == 1),
      n_med_perc = round(100*n_med/n(), 2),
      n_high = sum(severity == 2),
      n_high_perc = round(100*n_high/n(), 2),
      
      # Distribution by first pnc encounter
      n_pnc_4 = sum(pnc_wk == 4),
      pnc4_perc = round(100*n_pnc_4/n(),2),
      n_pnc_7 = sum(pnc_wk == 7),
      pnc7_perc = round(100*n_pnc_7/n(),2),
      n_pnc_16 = sum(pnc_wk == 16),
      pnc16_perc = round(100*n_pnc_16/n(),2),
      
      # Preterm birth
      n_preterm_all = sum(pregout_t_pre_miss >= 18 & pregout_t_pre_miss < 35),
      preterm_p = round(100*n_preterm_all / n(), 2),
      
      # Distribution of outcomes
      n_miscarriage_all = sum(pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss < 18),
      miscarriageall_p = round(100*n_miscarriage_all / n(),2),
      n_stillbirth_all = sum(pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss >= 18),
      stillbirthall_p = round(100*n_stillbirth_all/n(), 2),
      n_livebirth_all = sum(pregout_pre_miss == "livebirth"),
      livebirthall_p = round(100*n_livebirth_all/n()),
      
      # Timing of those outcomes
      miscarriageall_p25 = quantile(pregout_t_pre_miss[pregout_pre_miss == "fetaldeath" &
                                                         pregout_t_pre_miss < 18], 
                                    probs = 0.25)+2,
      miscarriageall_p75 = quantile(pregout_t_pre_miss[pregout_pre_miss == "fetaldeath" &
                                                         pregout_t_pre_miss < 18],
                                    probs = 0.75)+2,
      miscarriageall_med = median(pregout_t_pre_miss[pregout_pre_miss == "fetaldeath" &
                                                       pregout_t_pre_miss < 18])+2,
      
      stillbirthall_p25 = quantile(pregout_t_pre_miss[pregout_pre_miss == "fetaldeath" &
                                                        pregout_t_pre_miss >= 18],
                                   probs = 0.25)+2,
      stillbirthall_p75 = quantile(pregout_t_pre_miss[pregout_pre_miss == "fetaldeath" &
                                                        pregout_t_pre_miss >= 18],
                                   0.75)+2,
      stillbirthall_med = median(pregout_t_pre_miss[pregout_pre_miss == "fetaldeath" &
                                                      pregout_t_pre_miss >= 18])+2,
      
      livebirth_p25 = quantile(pregout_t_pre_miss[pregout_pre_miss == "livebirth"],
                               probs = 0.25)+2,
      livebirth_p75 = quantile(pregout_t_pre_miss[pregout_pre_miss == "livebirth"],
                               probs = 0.75)+2,
      livebirth_med = median(pregout_t_pre_miss[pregout_pre_miss == "livebirth"])+2,
      
      # Distribution of Preeclampsia
      n_preec_l32 = sum(preeclampsia_pre_miss == 1 & pregout_t_pre_miss < 30),
      n_preec_l32_p = round(100*n_preec_l32/n(), 2),
      n_preec = sum(preeclampsia_pre_miss == 1),
      n_preec_perc = round(100*n_preec/n(),2),
      preec_25 = quantile(pregout_t_pre_miss[preeclampsia_pre_miss == 1], probs=0.25)+2,
      preec_75 = quantile(pregout_t_pre_miss[preeclampsia_pre_miss == 1], probs=0.75)+2,
      preec_med = quantile(pregout_t_pre_miss[preeclampsia_pre_miss == 1], probs=0.50)+2,
      
      # Distribution of uncensored outcomes
      missing_mar = sum(ltfu_mar != "not"),
      missing_mar_perc = round(100*missing_mar/n(), 2),
      missing_mar_p25 = quantile(pregout_t_mar[ltfu_mar != "not"], probs = 0.25)+2,
      missing_mar_p75 = quantile(pregout_t_mar[ltfu_mar != "not"], probs = 0.75)+2,
      missing_mar_med = quantile(pregout_t_mar[ltfu_mar != "not"], probs = 0.5)+2,
      
      missing_mnar = sum(ltfu_mar_mnar != "not"),
      missing_mnar_perc = round(100*missing_mnar/n(), 2),
      missing_mnar_p25 = quantile(pregout_t_mar_mnar[ltfu_mar_mnar != "not"], probs=0.25)+2,
      missing_mnar_p75 = quantile(pregout_t_mar_mnar[ltfu_mar_mnar != "not"], probs = 0.75)+2,
      missing_mnar_med = quantile(pregout_t_mar_mnar[ltfu_mar_mnar != "not"], probs = 0.5)+2,
      
      .groups = 'keep'
    ) %>% 
    mutate(
      # Number of pregnancies per severity
      n_low = paste0(n_low," (", n_low_perc, "%)"),
      n_med = paste0(n_med," (", n_med_perc, "%)"),
      n_high = paste0(n_high," (", n_high_perc, "%)"),
      # Number of pregnancies per pnc
      n_pnc_4 = paste0(n_pnc_4, " (", pnc4_perc, "%)"),
      n_pnc_7 = paste0(n_pnc_7, " (", pnc7_perc, "%)"),
      n_pnc_16 = paste0(n_pnc_16, " (", pnc4_perc, "%)"),
      # Preterm birth
      n_preterm_all = paste0(n_preterm_all, " (", preterm_p, ")%"),
      # Pregnancy outcomes
      n_miscarriage_all = paste0(n_miscarriage_all, " (", miscarriageall_p,")%"),
      n_stillbirth_all = paste0(n_stillbirth_all, " (", stillbirthall_p, "%)"),
      n_livebirth_all = paste0(n_livebirth_all, " (", livebirthall_p, "%)"),
      # Timing of Preg Outcomes
      miscarriage_t = paste0(miscarriageall_med, " (", miscarriageall_p25, ", ", miscarriageall_p75, ")"),
      stillbirth_t = paste0(stillbirthall_med, " (", stillbirthall_p25, ", ", stillbirthall_p75, ")"),
      livebirth_t = paste0(livebirth_med, " (", livebirth_p25, ", ", livebirth_p75, ")"),
      # Preeclampsia
      n_preeclampsia = paste0(n_preec, " (", n_preec_perc, "%)"),
      preeclampsia_t = paste0(preec_med, " (", preec_25, ", ", preec_75, ")"),
      # Preeclampsia less than 32 weeks
      n_preeclampsia_l32 = paste0(n_preec_l32, " (", n_preec_l32_p, "%)"),
      # Missing by MAR
      missing_mar = paste0(missing_mar, " (", missing_mar_perc, "%)"),
      missing_mar_t = paste0(missing_mar_med, " (", missing_mar_p25, ", ", missing_mar_p75, ")"),
      # Missing by MNAR
      missing_mnar = paste0(missing_mnar, " (", missing_mnar_perc, "%)"),
      missing_mnar_t = paste0(missing_mnar_med, " (", missing_mnar_p25, ", ", missing_mnar_p75, ")") 
    ) %>% 
    select(scenario, trt, n_low, n_med, n_high, n_pnc_4, n_pnc_7, n_pnc_16,
           n_preterm_all, n_miscarriage_all,
           n_stillbirth_all, n_livebirth_all, miscarriage_t, stillbirth_t, livebirth_t,
           n_preeclampsia, preeclampsia_t, n_preeclampsia_l32,
           missing_mar, missing_mar_t, missing_mnar, missing_mnar_t
           ) %>% 
    pivot_longer(
      cols = !c(scenario, trt),
      names_to = "SummaryStatistic",
      values_to = "value"
    ) %>% 
    pivot_wider(
      names_from = c(scenario, trt),
      values_from = value
    ) %>% 
    kbl() %>% 
    kable_classic() %>% 
    add_header_above(c(" " = 1, "Non-Initiators" = 1, "Initiators" = 1)) %>% 
    #add_header_above(c(" " = 1, "Non-Initiators" = 1, "Initiators" = 1, "Non-Initiators" = 1, "Initiators" = 1)) %>% 
    add_header_above(c(" " = 1, "Test 1" = 2)) %>% 
    #add_header_above(c(" " = 1, "Test 1" = 2, "Test 2" = 2)) %>% 
    pack_rows("Number (%) of Pregnancies by Severity", 1, 3) %>% 
    pack_rows("Number (%) of Pregnancies by First PNC", 4, 6) %>% 
    pack_rows("Number (%) of Preterm Births", 7, 7) %>% 
    pack_rows("Number (%) of Pregnancy Outcomes", 8, 10) %>% 
    pack_rows("Median (IQR) of Pregnancy Outcome Timing", 11, 13) %>% 
    pack_rows("Number (%) of Pregnancies that Experienced Preeclampsia", 14, 14) %>% 
    pack_rows("Median(IQR) of Preeclampsia Timing", 15, 15) %>% 
    pack_rows("Number (%) of Pregnancies with Preeclampsia <32 weeks", 16, 16) %>% 
    pack_rows("Number (%) of Pregnancy Outcomes LTFU per MAR", 17, 17) %>% 
    pack_rows("Median (IQR) of LTFU Timing per MAR", 18, 18) %>% 
    pack_rows("Number (%) of Pregnancies LTFU per MAR+MNAR", 19, 19) %>% 
    pack_rows("Median (IQR) of LTFU Timing per MAR+MNAR", 20, 20)
      
  return(hold)
  
}


```

# Create table with description of prenatal care encounters

```{r}

  
describe_pnc <- function(dataset){
  
  hold <- dataset %>% #  test2 %>% # 
    mutate(
      n_pnc_before_pre_miss_outcome =
        sum(as.numeric(unlist(pnc_enc_rev)[1:pregout_t_pre_miss])==1),
      median_time_between_pnc = median(diff(which(unlist(pnc_enc_rev)[1:(pregout_t_pre_miss-1)]==1)), na.rm = TRUE),
      median_time_between_pnc = ifelse(is.na(median_time_between_pnc),
                                       0,
                                       median_time_between_pnc)
    ) %>%
    group_by(pnc_wk, pregout_t_pre_miss) %>% 
    summarize(
      
      n_median = median(n_pnc_before_pre_miss_outcome),
      n_q1 = quantile(n_pnc_before_pre_miss_outcome, probs = 0.25),
      n_q3 = quantile(n_pnc_before_pre_miss_outcome, probs = 0.75),
      
      time_between_median = median(median_time_between_pnc),
      time_between_q1 = quantile(median_time_between_pnc, probs = 0.25),
      time_between_q3 = quantile(median_time_between_pnc, probs = 0.75),
      
      .groups = 'keep'
    ) %>% 
    mutate(
      n = paste0(n_median," (", n_q1, ", ", n_q3, ")"),
      time_between = paste0(time_between_median, " (", time_between_q1,
                                   ", ", time_between_q3, ")")
    ) %>% 
    select(pnc_wk, pregout_t_pre_miss, n, time_between) %>% 
    kbl() %>% 
    kable_classic() %>% 
    add_header_above(c("Indexing Prenatal Encounter" = 1, " " = 1, 
                       "Median (IQR) Number of Prenatal Encounters" = 1,
                       "Median (IQR) Time Between Prenatal Encounters" = 1))
      
  return(hold)  
}


```


# Potential Outcomes

Describe the distribution of the generated potential outcomes at each gestational week. This can help understand if we're seeing an expected distribution of the generated data. This is a simple check that things look as expected. Not a clean kable. Not printed regularly as a result.

Note: There are 0 with fetal death among the untreated from gestational weeks 0-3. However, this occurs because that was a requirement for inclusion in the trial (i.e., no miscarriage prior to randomization).

```{r eval=FALSE}

# Number of distinct IDs is the number of rows of dataset
n_ids <- nrow(describe)

describe %>% 
  ungroup() %>% 
  select(scenario, id, preg_outcomes_untrt, preg_outcomes_trt) %>% 
  unnest(cols = c(preg_outcomes_untrt, preg_outcomes_trt)) %>% 
  unnest(cols = c(preg_outcomes_untrt, preg_outcomes_trt)) %>% 
  mutate(gw = rep(c(0:40), n_ids)) %>% 
  group_by(scenario, gw) %>% 
  summarize(
    n_contpreg_untrt = sum(preg_outcomes_untrt == "contpreg_next"),
    n_contpreg_trt = sum(preg_outcomes_trt == "contpreg_next"),
    n_fd_untrt = sum(preg_outcomes_untrt == "fetaldeath_next"),
    n_fd_trt = sum(preg_outcomes_trt == "fetaldeath_next"),
    n_lb_untrt = sum(preg_outcomes_untrt == "livebirth_next"),
    n_lb_trt = sum(preg_outcomes_trt == "livebirth_next"),
    .groups = 'drop'
  ) %>% 
  select(-scenario) %>% 
  kbl(col.names = c("GW", "Non-Initiators", "Initiators", "Non-Initiators", "Initiators", 
                    "Non-Initiators", "Initiators")) %>% 
  kable_classic() %>% 
  add_header_above(c(" " = 1, "Continue Pregnancy" = 2, "Fetal Death" = 2, "Live Birth" = 2)) %>% 
  pack_rows("Test 1", 1, 41) #%>% 
  #pack_rows("Test 2", 42, 82)




```

## Describe Cohort Ignoring Missingness

Look at the distribution of observed outcomes.

All outcomes, regardless of outcome type.

```{r}

describe %>% 
  mutate(Treatment = ifelse(trt == 0, 
                            "Non-Initiation", 
                            "Initiation")) %>% 
  ggplot(aes(x = (pregout_t_pre_miss+2), y = after_stat(density*width))) +
    geom_histogram(alpha = 0.2, position = "identity", bins = 41) +
    #geom_freqpoly(bins = 41) +
    facet_grid(scenario ~ Treatment, labeller = labeller(scenario = label_both, Treatment = label_value), switch = "y") +
  xlab("Gestational Week of Outcome from LMP") +
  ylab("Proportion of Respective Outcomes") +
  theme_bw()

```

All outcomes, stratified by outcome type.

```{r}


describe %>% 
  mutate(Treatment = ifelse(trt == 0, 
                            "Non-Initiation", 
                            "Initiation")) %>% 
  ggplot(aes(x = (pregout_t_pre_miss+2), y = after_stat(density*width), color = pregout_pre_miss, fill = pregout_pre_miss)) +
    geom_histogram(alpha = 0.2, position = "identity", bins = 41) +
    #geom_freqpoly(bins = 41) +
    facet_grid(scenario ~ Treatment, labeller = labeller(scenario = label_both, Treatment = label_value), switch = "y") +
  xlab("Gestational Week of Outcome from LMP") +
  ylab("Proportion of of Outcomes") +
  #scale_x_continuous(breaks = seq(4, 41, by =1)) +
  theme_bw()


```

Distribution of gestational age at miscarriage.

```{r}

table(subset(describe, pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss < 18)$pregout_t_pre_miss+2)

```

Distribution of gestational age at stillbirth.

```{r}

table(subset(describe, pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss >= 18)$pregout_t_pre_miss+2)

```

Distribution of gestational age at livebirth.

```{r}

table(subset(describe, pregout_pre_miss == "livebirth")$pregout_t_pre_miss+2)

```


## Distribution of Preeclampsia

```{r}

table(subset(describe, preeclampsia_pre_miss == 1)$pregout_t_pre_miss+2)


describe %>%
  filter(preeclampsia_pre_miss == 1) %>%
  mutate(Treatment = ifelse(trt == 0,
                            "Non-Initiation",
                            "Initiation")) %>%
  ggplot(aes(x = (pregout_t_pre_miss+2), y = after_stat(density*width))) +
  #ggplot(aes(x = (pregout_t_pre_miss+2))) +
    geom_histogram(alpha = 0.2, position = "identity", bins = 41) +
    #geom_freqpoly(bins = 41) +
    facet_grid(scenario ~ Treatment, labeller = labeller(scenario = label_both, Treatment = label_value), switch = "y") +
  xlab("Gestational Week of Preeclampsia from LMP") +
  ylab("Proportion of Preeclampsia Outcomes") +
  theme_bw()

```

# Summary Statistics

Now look at summary statistics for the cohort

## Whole Cohort

```{r}

describe_cohort(describe)

```

## Low Severity Disease

Describe characteristics of the overall cohort.

```{r}

describe_cohort(subset(describe, severity == 0))

```

Look at the timing of abortion according to the gestational age at cohort entry.

```{r}

low <- subset(describe, severity == 0)

low %>% 
  filter(pregout_pre_miss == 'fetaldeath' & pregout_t_pre_miss < 18) %>% 
  group_by((pnc_wk+2)) %>% 
  summarize(percent_of_pregnancies = round(100*n()/nrow(low), 2),
            percent_of_abortions = round(100*n()/nrow(subset(low, 
                                                             pregout_pre_miss == 'fetaldeath' & 
                                                               pregout_t_pre_miss < 18)), 2),
            min = min(pregout_t_pre_miss) + 2,
            p25 = quantile(pregout_t_pre_miss, 0.25) + 2,
            median = quantile(pregout_t_pre_miss, 0.50) + 2,
            p75 = quantile(pregout_t_pre_miss, 0.75) + 2,
            max = max(pregout_t_pre_miss) + 2
            )

```

## Medium Severity Disease

```{r}

describe_cohort(subset(describe, severity == 1))

```

## High Severity Disease

```{r}

describe_cohort(subset(describe, severity == 2))

```

# Distribution of Prenatal Care Encounters

```{r}

describe_pnc(describe)

```




```{r eval=FALSE}

# Focus on MAR + MNAR for now
test %>% 
  group_by(trt, severity) %>% 
  summarize(
    n = n(),
    # Distribution of outcomes
    n_miscarriage_all = sum(pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss < 20),
    n_stillbirth_all = sum(pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss >= 20),
    n_livebirth_all = sum(pregout_pre_miss == "livebirth"),
    # Distribution of observed outcomes
    n_miscarriage_obs = sum(pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss < 20 & ltfu_mar_mnar == "not"),
    n_stillbirth_obs = sum(pregout_pre_miss == "fetaldeath" & pregout_t_pre_miss >= 20 & ltfu_mar_mnar == "not"),
    n_livebirth_obs = sum(pregout_pre_miss == "livebirth" & ltfu_mar_mnar == "not"),
    # Distribution by first pnc encounter
    n_pnc_4 = sum(pnc_wk == 4),
    n_pnc_7 = sum(pnc_wk == 7),
    n_pnc_16 = sum(pnc_wk == 16),
    .groups = 'keep'
  )


```

